CDSR Human Data/Modelling Paper

### 2013-09-12 code/scenarios/cdsr/trunk/papers/ACS2013/main.tex
jk revised abstract, intro and section 2

Understanding these regions is crucial to joint intelligent action with humans.  Not only are these regions frequently tied to goals and commands: ``go to the front of the classroom'', ``defend the bottleneck'', and ``get to safety'', but they are also central to understanding human activities: e.g., ``Is there a class in session?''.

The long-term goal of our work is to create cognitive systems that can naturally interact with people in human environments.  While the study presented below illustrates the importance of context, object types and configurations, on human spatial judgements, constructing a cognitive systems approach requires more than reproducing these results.  First, the representational approach should be transferable to new contexts.  While humans do not demonstrate mastery after a single example of a concept, they are able to begin using it immediately refining it over time.  Second, the representation should be applicable in different reasoning tasks.  The functional nature of these regions makes them important for many tasks from action planning to activity recognition.

>>>>

Understanding these regions is crucial to joint intelligent action with humans; among other reasons they are frequently tieds to goals and commands: ``go to the front of the classroom'', ``defend the bottleneck'', and ``get to safety''. In the rest of the paper we present a study that examined the contextual dependence of these regions and dicuss the implications that these t. Following this we discuss the implications of these regions for the development of cognitive systems.

%JK Removed the following text and replaced with text above primarily to save space, feel free to switch back.
%  Not only are these regions frequently tied to goals and commands: ``go to the front of the classroom'', ``defend the bottleneck'', and ``get to safety'', but they are also central to understanding human activities: e.g., ``Is there a class in session?''.
%The long-term goal of our work is to create cognitive systems that can naturally interact with people in human environments.  While the study presented below illustrates the importance of context, object types and configurations, on human spatial judgements, constructing a cognitive systems approach requires more than reproducing these results.  First, the representational approach should be transferable to new contexts.  While humans do not demonstrate mastery after a single example of a concept, they are able to begin using it immediately refining it over time.  Second, the representation should be applicable in different reasoning tasks.  The functional nature of these regions makes them important for many tasks from action planning to activity recognition.
